### 2021-11-02 NSF2021/Description/specificaim1.tex
added a few notes to the NSF proposal

@@

\subsubsection{Analysis on the HAP model in terms of the HK functional}
The HK functional~\eqref{ansatz3} has had tremendous impact in
understanding biological membranes, but has received little attention in
terms of mathematical analysis. In the calculus of variations, the
principal question is whether a minimizer of an energy functional
exists. In the case of~\eqref{ansatz3}, the answer is presently unknown.
With regard to the simpler Canham-Helfrich energy,~\cite{Simon1993}
proved the existence of minimizing surfaces without boundary,
and~\cite{doi:10.1137/18M1195851} proved the well-posedness of a
spatially periodic, time-dependent elastic interface problem. An
analytical challenge for the HK functional~\eqref{ansatz3} is that
surface-director coupling makes it possible to have bounded energy
monolayers with corners, and such pathological examples must be ruled
out before carrying over the arguments for the Canham-Helfrich
functional to the present setting.

>>>>

\begin{itemize}
  \item Include ions in suspension
  \item Discussed in Sylvie Roke's talk---I added the slides to the repo
\end{itemize}

@@

\subsubsection{Analysis of the HAP model in terms of the HK functional}
The HK functional~\eqref{ansatz3} has transformed how scientists understand biological membranes, yet the
theory has received little attention in terms of
mathematical analysis. In the calculus of variations, the
principal question is whether a minimizer of an energy functional
exists. In the case of~\eqref{ansatz3}, the answer is presently unknown.
With regard to the simpler Canham-Helfrich energy,~\cite{Simon1993}
proved the existence of minimizing surfaces without boundary,
and~\cite{doi:10.1137/18M1195851} proved the well-posedness of a
spatially periodic, time-dependent elastic interface problem. An
analytical challenge for the HK functional~\eqref{ansatz3} is that
surface-director coupling makes it possible to have bounded energy
monolayers with corners, and such pathological examples must be ruled
out before carrying over the arguments for the Canham-Helfrich
functional to the present setting.

### 2021-11-02 NSF2021/Description/specificaim2.tex

\subsection{Specific Aim 2: Efficient, high-order methods for large-scale simulations}
% ----------------------------------------------------------------------
Over the past decade, there has been an explosion of interest in
small-scale processes that utilize capillary forces and van der Waals
interactions to coordinate movement
and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
Additionally, hydrodynamic interactions are central to fabricating complex,
three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
Hydrodynamic effects cannot
be ignored since they, like for the rates of biological functions 
like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
%
In Specific Aim 2, we propose to develop efficient high-order numerical
methods to simulate dynamic assembly of particles under HAP potential in
a viscous solvent. 
%
%
%hydrodynamics effects by em
%particles in a solvent. 
%
% Results from these proposed numerical simulations will be useful to 
% Finally, coarse-grained and molecular
%dynamics theories include water either explicitly or implicitly in their
%models. 
%
%The immediate goal of the present proposal is to simulate
%vesicle bilayers in external flows, where the bilayers are represented
%by a self-assembled collection of rigid particles.
%
As described in~\eqref{eq:stokes} and illustrated in
Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
equations for an incompressible, viscous fluid, and these equations are
coupled to the screened-Laplace equation~\eqref{SL} through viscous and
hydrophobic stress balance.

@@

\label{subsec:specific_aim_2}
%\begin{figure}[h]
\begin{wrapfigure}[14]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
    \vspace{-15pt}
    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity
    satisfies the Stokes equations, and the hydrophobic forces depend on
    the solvent activity that satisfies the screened Laplace equation.
    The geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
%\end{figure}
The HAP model requires solving exterior Dirichlet problems for the
screened Laplace equation and the Stokes mobility problem at each time
step in complex domains such as in Figure~\ref{fig:domain}. If
discretizing these equations with stencil-based numerical methods, the
computational domain must be truncated, the fluid volume must be
discretized, and artificial boundary conditions must be imposed. The
artificial boundary conditions introduce additional error, and
discretizing the volume results in an excessively large system of
equations. Moreover, it is difficult to obtain high-order
discretizations when the boundary surfaces are irregular. Alternatively,
since we are solving constant-coefficient linear elliptic
partial differential equations (PDEs), their
solutions can be represented with layer potentials
\begin{align}
  \label{eq:LP}
  u(\mathbf{x}) = \mathcal{K}[\sigma](\mathbf{x}) = 
  \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
  \sigma(\mathbf{y})\,dS,
\end{align}
where $\sigma$ is an unknown density function, and
$K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
of the PDE. By matching the prescribed boundary condition at
$\mathbf{x}_0 \in \partial\Omega$ with the limit of
equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a
boundary integral equation (BIE) for the density function is formed.

@@

% ----------------------------------------------------------------------
\subsubsection{Numerical issues}
\label{subsec:NumericalIssues}

>>>>

\subsection{Specific Aim 2: Efficient, high-order methods for large-scale simulations}
% ----------------------------------------------------------------------
Over the past decade, there has been an explosion of interest in
small-scale processes that utilize capillary forces and van der Waals
interactions to coordinate movement
and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
Additionally, hydrodynamic interactions are central to fabricate complex,
three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
Hydrodynamic effects cannot
be ignored since they, like for the rates of biological functions 
like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
%
In Specific Aim 2, we propose to develop efficient high-order numerical
methods to simulate dynamic assembly of particles under HAP potential in
a viscous solvent. 
%
%
%hydrodynamics effects by em
%particles in a solvent. 
%
% Results from these proposed numerical simulations will be useful to 
% Finally, coarse-grained and molecular
%dynamics theories include water either explicitly or implicitly in their
%models. 
%
%The immediate goal of the present proposal is to simulate
%vesicle bilayers in external flows, where the bilayers are represented
%by a self-assembled collection of rigid particles.
%
As described in~\eqref{eq:stokes} and illustrated in
Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
equations for an incompressible, viscous fluid, and these equations are
coupled to the screened-Laplace equation~\eqref{SL} through viscous and
hydrophobic stress balance.

@@

\label{subsec:specific_aim_2}
%\begin{figure}[h]
\begin{wrapfigure}[14]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
    \vspace{-15pt}
    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity
    satisfies the Stokes equations, and the hydrophobic forces depend on
    the solvent activity that satisfies the screened Laplace equation.
    The geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
%\end{figure}
The HAP model requires solving exterior Dirichlet problems for the
screened Laplace equation and the Stokes mobility problem at each time
step in complex domains such as in Figure~\ref{fig:domain}. If
discretizing these equations with stencil-based numerical methods, the
computational domain must be truncated, the fluid volume must be
discretized, and artificial boundary conditions must be imposed. The
artificial boundary conditions introduce additional error, and
discretizing the volume results in an excessively large system of
equations. Moreover, it is difficult to obtain high-order
discretizations when the boundary surfaces are irregular. Alternatively,
since we are solving constant-coefficient linear elliptic partial
differential equations (PDEs), the solutions can be represented with
layer potentials
\begin{align}
  \label{eq:LP}
  u(\mathbf{x}) = \mathcal{K}[\sigma](\mathbf{x}) = 
  \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
  \sigma(\mathbf{y})\,dS,
\end{align}
where $\sigma$ is an unknown density function, and
$K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
of the PDE. By matching the prescribed boundary condition at
$\mathbf{x}_0 \in \partial\Omega$ with the limit of
equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a
boundary integral equation (BIE) for the density function is formed.

@@

% ----------------------------------------------------------------------
\subsubsection{Numerical challenges}
\label{subsec:NumericalIssues}
